A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-01-30 paper.tex
break the figure out into two

%%% General usepackages, definitions, etc.
\usepackage[acronym,toc]{glossaries}
\usepackage{graphicx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{moreverb} % for verbatim snippets of code
\usepackage{fancyvrb}
\usepackage{tabularx} % for tables with line breaks
\usepackage{threeparttable} % for tables with notes
\usepackage[capitalize, noabbrev]{cleveref} % for reference multiple figures
\usepackage{calc} % allows for arithmetic on latex variables
\usepackage{float} % allows for figures to be placed explicitly
\usepackage{algorithm2e} % for algorithms
\usepackage{multirow} % combining rows in tables
\usepackage{footnote}
\usepackage{titlesec} % for using \titleformat
\usepackage{fixltx2e} % for using \textsubscript
\usepackage{bashful}
\usepackage{xspace}
\usepackage{color}
\usepackage{subfig}
\usepackage{minted}
%%%%%

@@

We herein present \code{aneris}' Python implementation, depicted in Figure
\ref{fig:software}, and conceptual, depicted in Figure \ref{fig:workflow}. The
library is composed of a number of utilities as well as three primary
components: the \texttt{HarmonizationDriver}, \texttt{Harmonizer}, and data
processing routines (shown in red, green, and blue, respectively in Figure
\ref{fig:software-workflow}).

@@

\begin{figure}
  \subfloat[Python Implementation\label{fig:software}]{
    \includegraphics[width=0.775\textwidth]{implementation_schematic.pdf}
    }
  \subfloat[Workflow\label{fig:workflow}]{
    \includegraphics[width=0.225\textwidth]{aneris-workflow.pdf}
    }
    \caption{ Panel \ref{fig:software} shows the various objects in the
      \code{aneris} code base as well as a short description of their scope of
      concern. Panel \ref{fig:workflow} displays the full harmonization process
      as executed by \code{aneris} for a single instance of a model and
      scenario. Operations that can be configured with user-based input
      configurations are shown in purple. Operations governed by the
      \texttt{HarmonizationDriver} are shown in red. Data processing operations
      are shown in blue. The core harmonization process, governed by the
      \texttt{Harmonizer} is shown in green.  }
    \label{fig:software-workflow}
\end{figure}

>>>>

%%% General usepackages, definitions, etc.
\usepackage[acronym,toc]{glossaries}
\usepackage{graphicx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{moreverb} % for verbatim snippets of code
\usepackage{fancyvrb}
\usepackage{tabularx} % for tables with line breaks
\usepackage{threeparttable} % for tables with notes
\usepackage[capitalize, noabbrev]{cleveref} % for reference multiple figures
\usepackage{calc} % allows for arithmetic on latex variables
\usepackage{algorithm2e} % for algorithms
\usepackage{multirow} % combining rows in tables
\usepackage{footnote}
\usepackage{titlesec} % for using \titleformat
\usepackage{fixltx2e} % for using \textsubscript
\usepackage{bashful}
\usepackage{xspace}
\usepackage{color}
\usepackage{subfig}
\usepackage{minted}
%%%%%

@@

We herein present \code{aneris}' Python implementation, depicted in Figure
\ref{fig:software}, and conceptual, depicted in Figure \ref{fig:workflow}. The
library is composed of a number of utilities as well as three primary
components: the \texttt{HarmonizationDriver}, \texttt{Harmonizer}, and data
processing routines (shown in red, green, and blue, respectively in Figures
\ref{fig:software} and \ref{fig:workflow}).

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{implementation_schematic.pdf}
    \caption[]{
      \label{fig:software}
      The various objects and their relation to one another in the \code{aneris}
      code base as well as a short description of their scope of concern.  
    }
  \end{center}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[height=0.8\textheight]{aneris-workflow.pdf}
    \caption[]{
      \label{fig:workflow}
The full harmonization process as executed by \code{aneris} for a single
instance of a model and scenario. Operations that can be configured with
user-based input configurations are shown in purple. Operations governed by the
\texttt{HarmonizationDriver} are shown in red. Data processing operations are
shown in blue. The core harmonization process, governed by the
\texttt{Harmonizer} is shown in green. }
  \end{center}
\end{figure}

%% \begin{figure}
%%   \subfloat[Python Implementation\label{fig:software}]{
%%     \includegraphics[width=0.775\textwidth]{implementation_schematic.pdf}
%%     }
%%   \subfloat[Workflow\label{fig:workflow}]{
%%     \includegraphics[width=0.225\textwidth]{aneris-workflow.pdf}
%%     }
%%     \caption{ Panel \ref{fig:software} shows the various objects in the
%%       \code{aneris} code base as well as a short description of their scope of
%%       concern. Panel \ref{fig:workflow} displays the full harmonization process
%%       as executed by \code{aneris} for a single instance of a model and
%%       scenario. Operations that can be configured with user-based input
%%       configurations are shown in purple. Operations governed by the
%%       \texttt{HarmonizationDriver} are shown in red. Data processing operations
%%       are shown in blue. The core harmonization process, governed by the
%%       \texttt{Harmonizer} is shown in green.  }
%%     \label{fig:software-workflow}
%% \end{figure}
